Designing Turk Experiments for Visual Statistical Inference

### 2013-06-02 paper_turk.tex
MTurk figure

>>>>

Figure \ref{fig:amazon_task} displays an example of such a task taken from their web site. In this task a worker just has to select from a pool of options and submit the task. The instructions are usually accompany the task and they are very simple and easy to follow.

\begin{figure}[htbp] 
   \centering
   \includegraphics[width=5in]{amazon_task.pdf} 
   \caption{An example of amazon mechanical turk task. Tasks are usually very simple and designed for human evaluations. With each task, simple instructions are given for workers to follow. The workers first accept the task before submitting their response.}
   \label{fig:amazon_task}
\end{figure}
